---
title: "Getting Started with binomial"
author: "Dev Navani"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Creating a binomial distribution model

To create a `"bindis"`, or binomial distribution object, you can use the function `bin_distribution()`. To do so, you need two inputs: 1) the number of trials, and 2) the probability of success.

```{r}
bindis <- bin_distribution(10, 0.5)
```

Here, we have created a model with trials equal to 10 and the probability of success equal to 0.5.

```{r}
bindis
```

The resulting object yields a data frame with two columns: number of successes and the associated probability of that event happening.


## Summary statistics

To find the summary statistics of certain binomial random variable, you will need to create another object called `"binvar"`.

```{r}
binvar <- bin_variable(10, 0.5)
binvar
```

Listed above are the supported summary stastistics for each specified binomial random variable (mean, variance, mode, skewness, kurtosis).

## Cumulative model

The `"bincum"` object is the same thing as the `"bindis"` object, except it keeps a cumulative column in its data frame as the number of successess are increased. 

```{r}
bincum <- bin_cumulative(10, 0.5)
bincum
```


## Plotting

Both the `"bindis"` and the `"bincum"` objects come with their own useful plotting functions, and their usage and output is displated below.

```{r}
bindis <- bin_distribution(10, 0.5)
plot(bindis)
```

```{r}
bincum <- bin_cumulative(10, 0.5)
plot(bincum)
```
