---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Overview

<!-- badges: start -->
<!-- badges: end -->

`"Binomial"` is a R package that implements functions for calculating probabilities of a binomial random variable. It also allows for related calculations such as the probability distributuion, the expected value, the variance, and more.

## Installation

You can install the released version of binomial from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("binomial")
```
The devlopment version is installed by:

``` r
install.packages("devtools")
devtools::install_github("stat133-sp19/hw-stat133-devnavani/blob/master/Workout03/binomial")
```

## Example

This is a basic example which shows you create a new binomial random variable.

```{r example}
library(binomial)
newRV = bin_variable(10, 0.5)
newRV
```

The summary statistics of this random variable can be found as well using the summary function.

```{r}
sum = summary(newRV)
sum
```


## Plotting and Tables

To make tables and plots representing a random variable, another class and function will be needed (one of bindis or bincum).

```{r cars}
newRV = bin_distribution(10, 0.5)
df <- attr(newRV, "data")
df
```

```{r}
plot(newRV)
```

```{r}
newRV = bin_cumulative(10, 0.5)
df <- attr(newRV, "data")
df
```

```{r}
plot(newRV)
```

